---
author: Oluwafemi Oyedele
date: '`r format(Sys.Date())`'
title: Augmented Design
output:
  html_document:
    toc_float: true
    theme: darkly
    toc: true
---

```{r setup, include = FALSE,echo=FALSE,message=FALSE,warning=FALSE,error=TRUE}
library(tidyverse)
library(readxl)
library(augmentedRCBD)
library(RColorBrewer)
library(corrr)
library(corrplot)
library(correlation)
knitr::opts_chunk$set(echo = TRUE)
```

## Market_quantitative

```{r,'42'}
market_quantitative <- read_excel(path = here::here('data/Phenotypic data_Joy updated.xlsx'),sheet = 'Market_quantitative') %>% janitor::clean_names()
```

## Convert all the Characters to Factor
```{r,'43'}
market_quantitative_tidy <- market_quantitative |> 
mutate(across(.cols=c(1:4),.fns=factor))

market_quantitative_tidy <- market_quantitative_tidy |> 
mutate(across(.cols=c(6:7),.fns=as.numeric))
```

## Stop 2


### Stop Here the model size is too large

### This is where we are having issues

## Fit the Model for Plant Height
```{r,'44',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$plant_height,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'45',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'plant_height_farm_quantitative.docx')
```


## Fit the Model for leaf_length
```{r,'46',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_length,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'47',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'leaf_length_farm_quantitative_DM.docx')

```
## Fit the Model for leaf_width
```{r,'48',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_width,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'49',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)


report.augmentedRCBD(aug = model1,target = 'leaf_width_market_quantitative.docx')
```


## Fit the Model for leaf_length_width_ratio
```{r,'50',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_length_width_ratio,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r,'51',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)



report.augmentedRCBD(aug = model1,target = 'leaf_length_width_market_quantitative.docx')

```
## Fit the Model for leaf_area
```{r,'52',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_area,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'53',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'leaf_area_market_quantitative.docx')

```
## Fit the Model for plant_span
```{r,'54',error=TRUE}

model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$plant_span,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'55',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'plant_span_market_quantitative.docx')

```
## Fit the Model for number_of_leaves_per_plant
```{r,'56',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_leaves_per_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'57',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'number_of_leaves_per_plant_market_quantitative.docx')

```
## Fit the Model for number_of_suckers_plant
```{r,'58',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_suckers_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'59',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'number_of_suckers_per_plant_market_quantitative.docx')

```
## Fit the Model for number_of_stolons_plant
```{r,'60',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_stolons_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'61',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'number_of_stolons_per_plant_market_quantitative.docx')

```
## Fit the Model for flower_formation
```{r,'62',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$flower_formation,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'63',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'flower_formation_market_quantitative.docx')

```
## Fit the Model for number_of_corms_hill
```{r,'64',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_corms_hill,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'65',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'number_of_corms_hill_market_quantitative.docx')

```
## Fit the Model for number_of_cormels_hill
```{r,'66',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_cormels_hill,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'67',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'number_of_cormels_hill_market_quantitative.docx')

```
## Fit the Model for total_weight
```{r,'68',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$total_weight,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'69',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'total_weight_market_quantitative.docx')

```
## Fit the Model for dry_matter
```{r,'70',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$dry_matter,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'71',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'dry_matter_market_quantitative.docx')

```
## Market_quantitative_DM
```{r,'72',error=TRUE}
market_quantitative_DM <- read_excel(path = here::here('data/Phenotypic data_Joy updated.xlsx'),sheet = 'Market_quantitative_DM')%>% janitor::clean_names() 
```

## Convert all the Characters to Factor
```{r,'73',error=TRUE}
market_quantitative_DM_tidy <- market_quantitative_DM %>% mutate(across(.cols=c(1:4),.fns=factor))
```

## Fit the Model for dry matter for market quantitative dry matter

```{r,'74',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_DM_tidy$block,treatment=market_quantitative_DM_tidy$collections,y=market_quantitative_DM_tidy$dry_matter,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```


## Descriptive Statistics of the Output
```{r,'80',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'dry_matter_market_quantitative_DM.docx')

```
