---
author: Oluwafemi Oyedele
date: '`r format(Sys.Date())`'
title: Augmented Design
output:
  html_document:
    toc_float: true
    theme: darkly
    toc: true
---

```{r setup, include = FALSE,echo=FALSE,message=FALSE,warning=FALSE,error=TRUE}
library(tidyverse)
library(readxl)
library(augmentedRCBD)
library(RColorBrewer)
library(corrr)
library(corrplot)
library(correlation)
knitr::opts_chunk$set(echo = TRUE)
```



## Farm_quantitative

```{r,'02'}
farm_qualitative <- read_excel(path = here::here('data/Phenotypic data_Joy updated.xlsx'),sheet = 'Farm_quantitative') %>% janitor::clean_names() %>% 
drop_na()
```

## Convert all the Characters to Factor
```{r,'03'}
farm_qualitative <- farm_qualitative %>% 
  mutate(across(.cols=c(1:4),.fns=factor))
```

## Fit the Model for days_to_emergence
```{r,'75'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$days_to_emergence,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r,'04'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'days_to_emergence_farm_quantitative.docx')
```

## Fit the Model for petiole_length
```{r,'05'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y =farm_qualitative$petiole_length,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r,'06'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'petiole_length_farm_quantitative.docx')
```

## Fit the Model for number_of_suckers_plant
```{r,'07'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y =farm_qualitative$number_of_suckers_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'08'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'number_of_suckers_plant_farm_quantitative.docx')
```


## Fit the Model for number_of_stolons_plant
```{r,'09'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y =farm_qualitative$number_of_stolons_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r,'10'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)


report.augmentedRCBD(aug = model1,target = 'number_of_stolons_plant_farm_quantitative.docx')
```

## Fit the Model for leaf_length
```{r,'11'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$leaf_length,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'12'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'leaf_length_farm_quantitative.docx')
```

## Fit the Model for leaf_width
```{r,'13'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$leaf_width,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r,'14'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'leaf_width_farm_quantitative.docx')
```

## Fit the Model for leaf_length_width_ratio
```{r,'15'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$leaf_length_width_ratio,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'16'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'leaf_length_width_farm_quantitative.docx')

```

## Fit the Model for leaf_area
```{r,'17'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$leaf_area,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r,'18'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'leaf_area_farm_quantitative.docx')
```

## Fit the Model for plant_height
```{r,'19'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$plant_height,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'20'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'plant_height_farm_quantitative.docx')
```


## Fit the Model for number_of_leaves_per_plant
```{r,'21'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$number_of_leaves_per_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'22'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'number_of_leaves_per_plant_farm_quantitative.docx')
```

## Fit the Model for plant_span
```{r,'23'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$plant_span,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'24'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)


report.augmentedRCBD(aug = model1,target = 'plant_span_farm_quantitative.docx')
```

## Fit the Model for flower_formation
```{r,'25'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$flower_formation,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'26'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'flower_formation_farm_quantitative.docx')
```

## Fit the Model for number_of_corms_hill
```{r,'27'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$number_of_corms_hill,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'28'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'number_of_corms_hill_farm_quantitative.docx')
```

## Fit the Model for number_of_cormels_hill
```{r,'29'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$number_of_cormels_hill,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'30'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'number_of_cormels_hill_farm_quantitative.docx')
```

## Fit the Model for total_weight
```{r,'31'}
model1 <- augmentedRCBD(farm_qualitative$block,treatment = farm_qualitative$collections,y=farm_qualitative$total_weight,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'32'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'total_weight_farm_quantitative.docx')
```


## Correlation Analysis for Farm Qualitative
```{r,'33'}
farm_qualitative_corr <- farm_qualitative %>% select(5:19)

corr <- correlation(farm_qualitative_corr,p_adjust = 'bonferroni',method = 'pearson',redundant = TRUE)

corr

 summary(object = corr,redundant = TRUE) 

```


## Colour
```{r,'34'}
col<- colorRampPalette(c("red", "white", "blue"))(20)
```

```{r,'35'}
M<-cor(farm_qualitative_corr)

corrplot(corr = M,method = 'circle',type = 'upper',order = 'hclust',tl.col = 'black',col=col)

```



```{r,'36'}
x <- correlate(farm_qualitative_corr)

#autoplot(x)

autoplot(x, triangular = "lower")

#autoplot(x, triangular = "full")
```

## Save the Plot
```{r,'37'}
ggsave(filename = 'farm_quantitative_Corr.png',path = here::here('plot'),width = 10,height = 10,dpi = 300,bg = 'white')
```



## Farm_quantitative_DM

```{r,'38'}
farm_quantitative_DM <- read_excel(path = here::here('data/Phenotypic data_Joy updated.xlsx'),sheet = 'Farm_quantitative_DM') %>% janitor::clean_names() %>% drop_na() 
```

## Convert all the Characters to Factor
```{r,'39'}
farm_quantitative_tidy <- farm_quantitative_DM %>% 
  mutate(across(.cols=c(1:4),.fns=factor))
```

## Fit the Model for dry matter for Farm Quantitative DM
```{r,'40'}
model1 <- augmentedRCBD(farm_quantitative_tidy$block,treatment =farm_quantitative_tidy$collections,y=farm_quantitative_tidy$dry_matter,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r,'41'}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'dry_matter_farm_quantitative_DM.docx')
```


## Market_quantitative

```{r,'42'}
market_quantitative <- read_excel(path = here::here('data/Phenotypic data_Joy updated.xlsx'),sheet = 'Market_quantitative') %>% janitor::clean_names()
```

## Convert all the Characters to Factor
```{r,'43'}
market_quantitative_tidy <- market_quantitative |> 
mutate(across(.cols=c(1:4),.fns=factor))

market_quantitative_tidy <- market_quantitative_tidy |> 
mutate(across(.cols=c(6:7),.fns=as.numeric))
```

## Stop 2


### Stop Here the model size is too large

### This is where we are having issues

## Fit the Model for Plant Height
```{r,'44',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$plant_height,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'45',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'plant_height_farm_quantitative_DM.docx')
```


## Fit the Model for leaf_length
```{r,'46',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_length,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'47',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)

report.augmentedRCBD(aug = model1,target = 'leaf_length_farm_quantitative_DM.docx')

```
## Fit the Model for leaf_width
```{r,'48',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_width,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'49',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)


report.augmentedRCBD(aug = model1,target = 'leaf_width_market_quantitative.docx')
```


## Fit the Model for leaf_length_width_ratio
```{r,'50',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_length_width_ratio,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```

## Descriptive Statistics of the Output
```{r,'51',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for leaf_area
```{r,'52',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$leaf_area,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'53',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for plant_span
```{r,'54',error=TRUE}

model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$plant_span,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'55',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for number_of_leaves_per_plant
```{r,'56',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_leaves_per_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'57',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for number_of_suckers_plant
```{r,'58',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_suckers_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'59',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for number_of_stolons_plant
```{r,'60',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_stolons_plant,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'61',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for flower_formation
```{r,'62',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$flower_formation,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'63',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for number_of_corms_hill
```{r,'64',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_corms_hill,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'65',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for number_of_cormels_hill
```{r,'66',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$number_of_cormels_hill,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'67',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for total_weight
```{r,'68',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$total_weight,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'69',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Fit the Model for dry_matter
```{r,'70',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_tidy$block,treatment=market_quantitative_tidy$collections,y=market_quantitative_tidy$dry_matter,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
## Descriptive Statistics of the Output
```{r,'71',error=TRUE}
augmentedRCBD::describe.augmentedRCBD(aug = model1)
```
## Market_quantitative_DM
```{r,'72',error=TRUE}
market_quantitative_DM <- read_excel(path = here::here('data/Phenotypic data_Joy updated.xlsx'),sheet = 'Market_quantitative_DM')%>% janitor::clean_names() 
```

## Convert all the Characters to Factor
```{r,'73',error=TRUE}
market_quantitative_DM_tidy <- market_quantitative_DM %>% mutate(across(.cols=c(1:4),.fns=factor))
```

## Fit the Model for dry matter for market quantitative dry matter

```{r,'74',error=TRUE}
model1 <- augmentedRCBD(market_quantitative_DM_tidy$block,treatment=market_quantitative_DM_tidy$collections,y=market_quantitative_DM_tidy$dry_matter,checks = c('Check 1','Check 2'),method.comp = 'tukey')
```
