---
title: "heritability2"
author: "Oluwafemi Oyedele"
date: "2023-02-09"
output: html_document
---



# Tuber Yield

# fit model ---------------------------------------------------------------
# random genotype effect

```{r,'10',cache=TRUE,dependson='dat1'}
g_ran <- lmer(data    = dat1,
formula = `tuber yield` ~ rep_number + (1|accession_name) + (1|rep_number:block_number))
```

# fixed genotype effect

```{r,'11',cache=TRUE,dependson='dat1'}
g_fix <- lmer(data    = dat1,
              formula = `tuber yield` ~ rep_number +    accession_name  + (1|rep_number:block_number))
```

# handle model estimates --------------------------------------------------
# genotypic variance component

```{r,'12',cache=TRUE,dependson='dat1'}
vc.g <- g_ran %>%
  VarCorr %>%
  as_tibble %>%
  filter(grp=="accession_name") %>%
  pull(vcov) # 0.1429021

vc.g
```
# mean variance of a difference between genotypes

```{r,'13',cache=TRUE,dependson='dat1'}
vdBLUE.avg <- g_fix %>%
  emmeans(pairwise ~ accession_name) %>%
  pluck("contrasts") %>%
  as_tibble %>%
  mutate(Var=SE^2) %>%
  pull(Var) %>%
  mean #

vdBLUE.avg
```

# H2 Piepho ---------------------------------------------------------------
```{r,'14',cache=TRUE,dependson='dat1'}
H2.p <- vc.g/(vc.g + vdBLUE.avg/2)
H2.p
```

# Average Tuber Weight

# fit model ---------------------------------------------------------------
# random genotype effect

```{r,'15',cache=TRUE,dependson='dat1'}
g_ran <- lmer(data    = dat1,
              formula = `Average tuber weight` ~ rep_number + (1|accession_name) + (1|rep_number:block_number))

```

# fixed genotype effect

```{r,'16',cache=TRUE,dependson='dat1'}
g_fix <- lmer(data    = dat1,
              formula = `Average tuber weight` ~ rep_number +    accession_name  + (1|rep_number:block_number))
```

# handle model estimates --------------------------------------------------
# genotypic variance component

```{r,'17',cache=TRUE,dependson='dat1'}
vc.g <- g_ran %>%
  VarCorr %>%
  as_tibble %>%
  filter(grp=="accession_name") %>%
  pull(vcov) # 0.1429021

vc.g
```
# mean variance of a difference between genotypes

```{r,'18',cache=TRUE,dependson='dat1'}
vdBLUE.avg <- g_fix %>%
  emmeans(pairwise ~ accession_name) %>%
  pluck("contrasts") %>%
  as_tibble %>%
  mutate(Var=SE^2) %>%
  pull(Var) %>%
  mean #

vdBLUE.avg
```

# H2 Piepho ---------------------------------------------------------------
```{r,'19',cache=TRUE,dependson='dat1'}
H2.p <- vc.g/(vc.g + vdBLUE.avg/2)
H2.p
```

# Tuber Length

# fit model ---------------------------------------------------------------
# random genotype effect

```{r,'20',cache=TRUE,dependson='dat1'}
g_ran <- lmer(data    = dat1,
              formula = `Tuber lengt` ~ rep_number + (1|accession_name) + (1|rep_number:block_number))

```

# fixed genotype effect

```{r,'21',cache=TRUE,dependson='dat1'}
g_fix <- lmer(data    = dat1,
              formula = `Tuber lengt` ~ rep_number +    accession_name  + (1|rep_number:block_number))
```

# handle model estimates --------------------------------------------------
# genotypic variance component

```{r,'22',cache=TRUE,dependson='dat1'}
vc.g <- g_ran %>%
  VarCorr %>%
  as_tibble %>%
  filter(grp=="accession_name") %>%
  pull(vcov) # 0.1429021

vc.g
```
# mean variance of a difference between genotypes

```{r,'23',cache=TRUE,dependson='dat1'}
vdBLUE.avg <- g_fix %>%
  emmeans(pairwise ~ accession_name) %>%
  pluck("contrasts") %>%
  as_tibble %>%
  mutate(Var=SE^2) %>%
  pull(Var) %>%
  mean #

vdBLUE.avg
```

# H2 Piepho ---------------------------------------------------------------
```{r,'24',cache=TRUE,dependson='dat1'}
H2.p <- vc.g/(vc.g + vdBLUE.avg/2)
H2.p
```
# rAUDPCYMV

# fit model ---------------------------------------------------------------
# random genotype effect

```{r,'25',cache=TRUE,dependson='dat1'}
g_ran <- lmer(data    = dat1,
              formula = rAUDPCYMV ~ rep_number + (1|accession_name) + (1|rep_number:block_number))

```

# fixed genotype effect

```{r,'26',cache=TRUE,dependson='dat1'}
g_fix <- lmer(data    = dat1,
              formula = rAUDPCYMV ~ rep_number +    accession_name  + (1|rep_number:block_number))
```

# handle model estimates --------------------------------------------------
# genotypic variance component

```{r,'27',cache=TRUE,dependson='dat1'}
vc.g <- g_ran %>%
  VarCorr %>%
  as_tibble %>%
  filter(grp=="accession_name") %>%
  pull(vcov) # 0.1429021

vc.g
```
# mean variance of a difference between genotypes

```{r,'28',cache=TRUE,dependson='dat1'}
vdBLUE.avg <- g_fix %>%
  emmeans(pairwise ~ accession_name) %>%
  pluck("contrasts") %>%
  as_tibble %>%
  mutate(Var=SE^2) %>%
  pull(Var) %>%
  mean #

vdBLUE.avg
```

# H2 Piepho ---------------------------------------------------------------
```{r,'29',cache=TRUE,dependson='dat1'}
H2.p <- vc.g/(vc.g + vdBLUE.avg/2)
H2.p
```


